\documentclass[10pt, letterpaper]{article}

\usepackage{amsmath}
\usepackage{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{listings}

\geometry{
	a4paper,
	left=1in,
	right=1in,
	bottom=1in,
	top=1in,
}

\titlespacing{\section}
{0pt} %left
{0pt} % before sep
{0pt} % after sep

\titlespacing{\subsection}
{0pt}
{0pt}
{0pt}

\begin{document}
\thispagestyle{empty}
\begin{center}
	\textbf{\huge{Aiden Wenzel}}
	\vspace{3pt}

	Ann Arbor, MI \hspace{5pt} (248)-775-9622 \hspace{5pt} wenzel.aiden@outlook.com \hspace{5pt} github.com/aiden-wenzel
\end{center}

\section*{Objective}
\hrule
\vspace{3pt}
\noindent Summer 2026 Internship in Embedded Systems or Circuit Design


\section*{Education}
\hrule
\vspace{3pt}

\subsection*{University of Michigan}
\begin{itemize}[label={}, leftmargin=0pt, itemsep=0pt, parsep=0pt, topsep=0pt]
	\item Ann Arbor, MI (September 2023 - May 2027)
	\item BSE, Electrical Engineering
	\item Minor, Computer Science and Music
	\item GPA: $3.45/4.00$
\end{itemize}

\section*{Experience}
\hrule
\vspace{3pt}

\subsection*{Coretek}
\begin{itemize}[label={}, leftmargin=0pt, itemsep=0pt, parsep=0pt, topsep=0pt]
	\item Farmington, MI (May 2024 - July 2025)
	\item Technical Support Specialist
	\item Worked with HTML, CSS, and C\# to develop intuitive ASP.NET UIs.
	\item Used C\# APIs to pull customer data from MS Azure ServiceNow.
	\item Used KQL to query and summarize cloud resource analytics in Azure dashboards.
\end{itemize}

\section*{Projects}
\hrule
\vspace{3pt}
\subsection*{Fractal Visualizer $\vert$ C++}
\begin{itemize}[label={}, leftmargin=0pt, itemsep=0pt, parsep=0pt, topsep=0pt]
	\item Utilized OpenGL APIs to accurately visualize the Mandelbrot set and Julia sets.
	\item Implemented custom panning and zoom functionality for near-infinite zooming into complex geometries.
\end{itemize}

\subsection*{Conway's Game of Life $\vert$ C++}
\begin{itemize}[label={}, leftmargin=0pt, itemsep=0pt, parsep=0pt, topsep=0pt]
	\item Wrote custom implementation of Conway's Game of Life using SDL.
	\item Customized build system and dependency management with CMake.
\end{itemize}

\subsection*{Instrument Recognition Software $\vert$ Python}
\begin{itemize}[label={}, leftmargin=0pt, itemsep=0pt, parsep=0pt, topsep=0pt]
	\item Worked with a team of 3 other engineering students to build an instrument recognition app.
	\item Processed audio data using Librosa library with feature extraction algorithms like the FFT.
	\item Trained CNN with processed audio data to predict what musical instrument is featured in the sample.
\end{itemize}


\section*{Skills}
\hrule
\vspace{3pt}

\subsection*{Programming}
\begin{itemize}[label={}, leftmargin=0pt, itemsep=0pt, parsep=0pt, topsep=0pt]
	\item Matlab: Organized data, processed images, and plotted data.
	\item C++: Substantial knowledge of STL. Implemented algorithms and data structures from scratch.
	\item C: Programmed embedded control systems for autonomous robots.
	\item Python: Built deep learning models with PyTorch. Processed data with Pandas, NumPy, and Matplotlib.
	\item \LaTeX: Wrote elegant, concise lab reports and homework assignments.
\end{itemize}

\subsection*{Unix}
\begin{itemize}[label={}, leftmargin=0pt, itemsep=0pt, parsep=0pt, topsep=0pt]
	\item Worked with Debian-based Linux distributions such as Ubuntu and Mint.
	\item Familiar with terminal-based text editing using Vim.
	\item Experience with basic terminal utilities such as \lstinline{grep}, \lstinline{git}, \lstinline{make}, and \lstinline{tmux}.
\end{itemize}

\subsection*{Circuit Analysis}
\begin{itemize}[label={}, leftmargin=0pt, itemsep=0pt, parsep=0pt, topsep=0pt]
	\item Waveforms: Analyzed analog signals in AC and DC circuits with an Oscilloscope.	
	\item LTspice: Simulated analog circuits.
	\item Logisim: Simulated digital logic circuits.
	\item ModelSim: Simulated digital logic circuits using Verilog HDL.
\end{itemize}

\section*{Extracurriculars}
\hrule
\vspace{3pt}

\subsection*{Michigan Marching Band}
\begin{itemize}[label={}, leftmargin=0pt, itemsep=0pt, parsep=0pt, topsep=0pt]
	\item Dedicated approximately 20 hours each week to rehearsals and performances in the Big House.
	\item Performed at the Big Ten Championship in 2023 and the ReliaQuest Bowl in 2024.
	\item Initiated as an official brother of $KK\Psi$, the National Honorary Band Fraternity.
	\item Performed with the Michigan Hockey Band at Yost Ice Arena.
\end{itemize}

\end{document}
